\documentclass{article}

\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[top=1cm, bottom=1cm, outer=2cm, inner=2cm]{geometry}

\pagenumbering{gobble}

\titleformat{\section}[frame]
{\huge}
{}
{.25em}
{\filcenter\bfseries\lowercase}

\titlespacing{\section}
{0em}{1em}{1em}

\titleformat{\subsection}
{\bfseries\Large}
{\hspace{-.25in}$\bullet$}
{0em}
{}

\titlespacing{\subsection}
{0em}{1em}{.5em}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{0em}
{}[---]

\titlespacing{\subsubsection}
{0em}{0em}{0em}

\renewcommand{\maketitle}{\begin{center}
{\huge\bfseries
\theauthor}
\vspace{.25em}
gyzmoify@gmail.com
\end{center}
}

\begin{document}

\title{\LaTeX}
\author{gyzmoify (Paige)}

\maketitle

\section{intro}

Hello there.
My name is Paige.
Feeling horny? Let me help make it worse.

\subsection{hobbies}

\begin{itemize}
    \item Sci-Fi
    \item Chess
    \item Computers
    \item Operating Systems
    \item Automation
    \item Scripting
    \item Programming
    \item \href{https://www.archlinux.org/}{Arch Linux}
    \item \href{https://www.rust-lang.org/}{Rust Language}
    \item \href{https://haxe.org/}{Haxe Language}
    \item \href{https://www.python.org/}{Python Language}
\end{itemize}

I'm running Arch Linux and i3wm on my machine.
Always looking for ways to add another hotkey or write another script to do another thing.

\subsection{sexual development}

My sexual adventure started with a gravitation towards tight clothing in general.
I fell in love with the nice gentle feeling of soft fabric rubbing on my parts.
This eventually transitioned into a full wedgie fetish.
When I first discovered masturbation I was already avoiding orgasms without even knowing what they would feel like.
All I knew was, the more I played with myself, the more sensitive I would get.
I was scared of what might happen if I became too sensitive so I would always stop before cumming.
Then after having a number of orgasms accidentally, I knew how they felt, and I liked it.
Things flipped and I started trying to make myself more sensitive much more often.
At some point, pain became a large part of making myself more sensitive.
Then I started using crotch ropes (because they're really just wedgie with rope) as a way to transition into bondage.
Having other people tell me I couldn't cum reminds me of when I first started learning about myself and that really turns me on, but with one large difference.
Now, instead of avoiding too much sensitivity (orgasms) out of fear, I enjoy becoming as sensitive as possible without cumming, even to the point where I cry.
Orgasms always were, and still are, an object to be avoided; either by my own will or the will of others.
This speaks in some way to the specific type of cruelty I seek in most partners.
These days, it's extremely rare for me to have a full orgasm and I prefer to stay in the desperate sensitive tormented powertripping headspace that I unknowingly avoided as a teenager as often as possible.

\subsection{physical qualities}

red hair, green eyes, pale white skin, 5'8, 128lbs, 32c, waxed/shaved
Tattoo on my left forearm \textgreater{} ''!/bin/sh''

\subsection{session flow}

Tease me, torture me, make me edge, ruin me; but never give me a full orgasm.
I thrive when I'm edging and in pain.
In fact, the edging essentially just happens as a symptom of the right kind of pain.
Definitely do not let me have a full orgasm ever no matter what.
If you make me cry, simply continue. Simply punish me for crying.
Crying for me is just a release. You may think of it as the only way I'm allowed to cum.

Porn:
I love having to watch a girl have either a full or ruined orgasm.
Especially if it's forced in bondage.
You'll find links to my main sources of porn in the resources section below.

Ruins:
I do enjoy them. They make me crazy in a good way. But they should be rare.
Making me ruin multiple times in a row is a great way to push me into subspace where nothing outside of that experience exists.

\newpage

\section{positions}

\subsection{hanging wedgie}

Hang by either the back or front of my panties.
Sometimes both at the same time.
I tend to prefer frontals just because they tend to be much more painful.

\subsection{shoulder wedgie}

Pull the sides of my panties up over my shoulders.
This is helpful for something mobile and easy that stays in place.
You can think of it like a really tight leotard.

\subsection{floss wedgie}

Continuously sliding my panties so that they rub my clit.
Eventually the friction may become painful.

\subsection{triangle}

Place one clamp on each nipple and one on my clit.
Then I connect them with rope or string so they pull on each other.
This forms the shape of a triangle.

\subsection{choking}

Thread a belt through the legholes in the back of my panties.
Clasp the belt around the front of my neck.
Now the belt is pulling up the back of my panties and choking me at the same time.
Humping my pillow or something similar in this position can be quite interesting.

\subsection{primary}

This position is meant to be the most pain possible.
Normally meant to be used at the height of an especially intense session.
Tiger balm is applied to my clit and nipples.
Stinging nettles and itching powder are placed in my panties.
My breasts are tied.
Crotch rope is tied under my panties to keep my clit exposed so it can't escape the torture.
One pair of panties in a shoulder wedgie, with a belt looped around the front of my neck and the legholes on my back.
A second pair of panties in a hanging frontal wedgie.
The ``triangle'' clamp pattern is applied on the outside of the panties.

\subsection{secondary}

This position is meant to be something I can walk in and still experience a decent amount of discomfort.
Tiger balm is applied to my clit and nipples.
Panties are pulled over my shoulders (shoulder wedgie).
Crotch rope is tied over panties.

\subsection{tertiary}

This position is meant to be something relatively uncomfortable I can wear in public without being noticed.
Secondary with clothes on top to hide it.
Dom must specify which clothes to wear.
Tight bottoms are worn to keep things in place.
\href{https://freddystore.com/collections/freddy-wrup-pants}{Wrup pants} are currently my favorite for this.

\subsection{pussy spanking game}

This game was originally designed to give me a very unlikely chance to cum.
However, it now sits in this file as a placeholder and is in need of a revamp.
I've reached a point where I can honestly say that nobody should ever let me cum.
Ever.
Not even as a very small chance.

\newpage

\section{resources}

\subsection{porn}

These links will bring you to where I generally look for porn.
The first is a scrolller link I constructed myself.
The second is a tumbex link which loads content from my tumblr page.
I do have a decent amount of porn saved and have written a discord bot and web page which are capable of displaying my collection to the internet.
I don't keep these services running all the time.
Feel free to ask me about either and I may start them.
It doesn't take long.

\href{https://scrolller.com/r/goddesses+Sexyness+overknees+Womenorgasm+CosplayBeauties+cosplaybutts+cuckoldcaptions+femdomcaptions+sissycaptions+HandsInPanties+PussyWedgie+quiver+forcedorgasms+cameltoe+RuinedOrgasms+postorgasm+orgasmcontrol+panties+leotards+FayeReagan+WedgieGirls+sybian+shinybondage+HoldingIt+OnePieceSuits+NSFWTiedTogether+teaseonly+leotard+WYCSTVTTU+ExtremeCameltoe+hipcleavage+fithips+boyshorts+girlsinyogashorts+lingerie+Playboy+gettingherselfoff+YogaPants+TightShorts+girlsinyogapants+femdom_gifs+TooCuteForPorn+DarkAngels+Ebony+OrgasmTorture}{Scrolller - Pulls content from reddit.}

\href{https://www.tumbex.com/gyzmoify.tumblr/posts}{Tumbex - Pulls content from tumblr.}

\subsection{tools}

\begin{itemize}
    \item panties
    \item tiger balm
    \item icy hot
    \item toothpaste
    \item itching powder
    \item stinging nettle
    \item hemp rope
    \item nylon rope
    \item electric clamps
\end{itemize}

I have eight electric clamps.
They connect to the main unit in pairs of two.
The main unit has four knobs which each varry in power from 0 (off) to 100 (full power)

\subsection{rules}

For free days alone when no partners are online to play with.

\begin{itemize}
    \item Floss while home and waiting for something.
    \item While home, shoulder wedgie at all times. Exceptions: restroom, sleeping.
    \item Tertiary when out of the house.
    \item 5 pussy spanks for each edge.
    \item Ruin all accidental orgasms.
    \item Ruin whenever partner has a full orgasm.
\end{itemize}

\subsection{partners}

I have a sister and she sometimes will offer a second set of hands.
Our relationship first became sexual at the start of 2015.
At that time, I was 22 and she was 21.
Both of our schedules can be unpredictable at times so availability may change at any time.

\end{document}
